Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-07-13 manuscript/ms.tex
Minor

{\bf Ensembler} is written in Python, and can be used via a command-line tool ({\tt ensembler}) or via a flexible Python API to allow integration of its components into other applications.
All command-line and API information in this article refers to the \href{https://github.com/choderalab/ensembler/tree/v1.0}{version 1.0 release of Ensembler}.
Up-to-date documentation can be found at \href{http://ensembler.readthedocs.org/en/latest/}{ensembler.readthedocs.org}.

@@

The resultant models are available as part of a supplementary dataset which can be downloaded from the Dryad Digital Repository (DOI: \href{https://dx.doi.org/10.5061/dryad.7fg32}{10.5061/dryad.7fg32}).

>>>>

{\bf Ensembler} is written in Python, and can be used via a command-line tool ({\tt ensembler}) or via a flexible Python API to allow integration of its components into other applications.
All command-line and API information in this article refers to the \href{https://github.com/choderalab/ensembler/tree/v1.0.2}{version 1.0.2 release of Ensembler}.
Up-to-date documentation can be found at \href{http://ensembler.readthedocs.org/en/latest/}{ensembler.readthedocs.org}.

@@

The resultant models are available as part of a supplementary dataset which can be downloaded from the Dryad Digital Repository (DOI: \href{http://datadryad.org/review?doi=doi:10.5061/dryad.7fg32}{10.5061/dryad.7fg32}).
